---
title: "phenMap"
author: "Gengping Zhu"
date: "2023-10-17"
output: md_document
---

## install and loading packages
```{r}
library(devtools)
install_github('gpzhu/PhenMap')

library(phenMap)
library(terra)
library(rgdal)
library(raster)

library(rnaturalearth)
library(rnaturalearthdata)
```


## read system file in phenMap package
```{r}
tmax <-rast(system.file("extdata", "tmax.tif", package="phenMap"))
tmin <-rast(system.file("extdata", "tmin.tif", package="phenMap"))
tavg<-rast(system.file("extdata", "tavg.tif", package="phenMap"))
```

### read globe polygon map
```{r}
glb <- ne_countries(scale = "medium", returnclass = "sp")
```

#### Mapping number of generation based on basal temperature and growing degree days

# DVD0 basal temperature/low threshold development temperature, based on which insect start to develop
# GDD growing degree days of egg to adult
# stk, which is stack raster of grid daily mean temperature, SpatRaster object (1-365 days basis)

```{r}
gen<-Gen(DVD0=10, GDD=60, stk=tavg) ##This is the parameter of coding moth
```


```{r}
gen<-Gen(DVD0=10, GDD=60, stk=tavg) ##This is the parameter of coding moth
```

#### Mapping emergence date of insect after overwintering

# tasmax stack raster of grid daily maximum temperature, SpatRaster object (1-365 days basis)
# tasmin stack raster of grid daily minimum temperature, SpatRaster object (1-365 days basis)
# DVD0 basal temperature/low threshold development temperature, based on which insect start to develop
# GDD growing degree days of egg to adult


```{r}
emg<-emerg(DVD0=10, GDD=60, tasmax=tmax, tasmin=tmin) ##This is the parameter of coding moth
```

## Plot of number of generation
```{r}
plot(gen)
plot(glb,add=T)
```

## Plot of emergence date
```{r}
plot(emg)
plot(glb,add=T)
```
